Network Configuration Synthesis with Abstract Topologies

### 2016-11-12 paper/abstraction/paper.tex
adding figure
edits

\subsection{Compilation}

@@

%In practice, operators would often like to reason about a variety of properties for, not only their current network topology, but also future versions of it.
The Product Graph provides a convenient representation to capture the joint impact of both topology and routing policy. In this section we present an analysis that operates over the abstract Product Graph to find a lower bound on the number of disjoint paths between pairs of concrete nodes. Answering questions about the number of disjoint paths between nodes allows operators to reason about many useful network properties such as reachability (\IE, is there at least one path) and fault tolerance (\EG, how many failures will disconnect certain routers).

@@

\subsection{Abstract k-disjoint paths}
\label{sec:property-checking}

\dpw{we could flip the order of this description:  give simple concrete $S_A(j,k)$ first and
then go to the general.}
To infer bounds on the number of disjoint paths between concrete nodes we use information about the structure of the underlying concrete topologies encoded in abstraction constraints.
%
The idea is to maintain, for each node in the abstract Product Graph, facts learned about the number of disjoint paths to some number of concrete routers in the node's role. More specifically, we maintain facts of the form:
%
\[ \begin{array}{c}
  L_{X_1}, \ldots, L_{X_n}(j,k)
\end{array} \]
\noindent
%
Each label $L \in \{S,A\}$ is either $S$, which stands for "some" or is $A$, which stands for "all". There is one label for each pod in the abstraction pod hierarchy. For a given node, $L_{X_1}$ corresponds to the outermost pod, $L_{X_{n-1}}$ corresponds to the innermost pod, and $L_{X_n}$ to the the node itself.

Semantically, $L_{X_1}, \ldots, L_{X_n}(j,k)$ means that starting from some concrete source node, for "some"/``all" pods $X_1$, $L_{X_2}, \ldots, L_{X_n}(j,k)$ holds. The base case $L_{X_n}(j,k)$ means that for "some"/``all" groups of size $j$ concrete routers, there are $k$ edge-disjoint paths to each such that all $j*k$ paths are disjoint.
%
For example, a fact of the form: $A_P, S_{TL}(2,4)$ means that for all pods P, there is some group of 2 concrete routers in role TL such that they each have 4 disjoint paths to them from the source and all 8 paths are disjoint.

@@

The first rule, \infrule{I-out1} applies to a learned fact of the form L$(j,k)$ where the number of outgoing edges from any concrete node in the $m$ role is greater than 0. In the worst case, the largest group of concrete nodes we could hope to reach at the $n$ role would be $e_1$ since all j nodes at the bottom may have the same outgoing edges to the concrete nodes at the top. Furthermore, the total number of disjoint paths to the $j$ nodes at the bottom is equal to $j*k$. Since adding edges between the nodes keeps the existing paths disjoint, and since we can not exceed the current number of disjoint paths to the concrete nodes in role $m$ on the bottom, the largest reachable group for the top node will be $min(j*k,e_1)$. Since we do not know for certain that all $j$ nodes have outgoing edges to the same nodes at the top, we conservatively use $1$ for the number of disjoint paths to each node on top.

@@

%By combining the tagging, filtering and preference mechanisms, we can generate safe BGP configurations. In general, configurations are generated by combining the per-prefix configurations in the same order specified in the policy.
Figure~\ref{fig:bgp-configs} shows part of the final configuration for spine routers for the concrete and abstract policies in a vendor-neutral syntax.
%
For prefix $\True$ ($0.0.0.0/[0..32]$), the spine routers will match advertisements from peer N1 and N2. The match for N1 is preferred since it has a higher BGP local-preference attribute (110). If an advertisement from N1 is available the spine uses this and attaches the community tag $(1,0)$ before sending the route to all its peers. If an advertisement is only available from the backup N2, then it attaches the tag $(0,1)$ instead.
%
The template configuration matches any global prefix $\CD{\$GP}$ from any internal peer and re-advertise the route to all of its peers ($*$). For any local prefix it will allow an advertisement from any internal peer, and re-advertise the route to only other internal peers. The concrete configurations have a similar configuration for each local and global prefix.

>>>>

\subsection{Compilation}
\label{subsec:compilation}

@@

%In practice, operators would often like to reason about a variety of properties for, not only their current network topology, but also future versions of it.
%% The Product Graph provides a convenient representation to capture the joint impact of both topology and routing policy. In this section we present an analysis that operates over the abstract Product Graph to find a lower bound on the number of disjoint paths between pairs of concrete nodes. Answering questions about the number of disjoint paths between nodes allows operators to reason about many useful network properties such as reachability (\IE, is there at least one path) and fault tolerance (\EG, how many failures will disconnect certain routers).

@@

%\subsection{Abstract k-disjoint paths}
%\label{sec:property-checking}

%
To infer bounds on the number of disjoint paths between concrete nodes we use information about the structure of the underlying concrete topologies encoded in abstraction constraints.
%
As discussed informally in~\ref{subsec:compilation},
for each node in the abstract Product Graph, 
the idea is to maintain facts learned about the number of disjoint paths 
to some number of concrete routers in the node's role. 
More specifically, we maintain facts of the form:
%
\[ \begin{array}{c}
  L_{X_1}, \ldots, L_{X_n}(j,k)
\end{array} \]
\noindent
%
where each label $L \in \{S,A\}$ is either $S$, which stands for "some" or is $A$, which stands for "all". There is one label for each pod in the abstraction pod hierarchy. For a given node, $L_{X_1}$ corresponds to the outermost pod, $L_{X_{n-1}}$ corresponds to the innermost pod, and $L_{X_n}$ to the the node itself.
Semantically, $L_{X_1}, \ldots, L_{X_n}(j,k)$ means that starting from some concrete source node, for some/all pods $X_1, \ldots, X_{n-1}$
and for some/all groups of nodes in the role $X_n$ of size $j$,
%, $L_{X_2}, \ldots, L_{X_n}(j,k)$ holds. The base case $L_{X_n}(j,k)$ means that for "some"/``all" groups of size $j$ concrete routers, 
there are $k$ paths to each such that all $j*k$ paths are edge-disjoint.
%
%For example, a fact of the form: $A_P, S_{TL}(2,4)$ means that for all pods P, there is some group of 2 concrete routers in role TL such that they each have 4 disjoint paths to them from the source and all 8 paths are disjoint.

@@

The first rule, \infrule{I-out1} applies to a learned fact of the form $L_m(j,k)$ where the number of outgoing edges from any concrete node in the $m$ role is greater than 0. In the worst case, the largest group of concrete nodes we could hope to reach at the $n$ role would be $e_1$ since all j nodes at the bottom may have outgoing edges to the same concrete nodes at the top. Furthermore, the total number of disjoint paths to the $j$ nodes at the bottom is equal to $j*k$. Since adding edges between the nodes keeps the existing paths disjoint, and since we can not exceed the current number of disjoint paths to the concrete nodes in role $m$ on the bottom, the largest reachable group for the top node will be $min(j*k,e_1)$. Since we do not know for certain that all $j$ nodes have outgoing edges to the same nodes at the top, we conservatively use $1$ for the number of disjoint paths to each node on top.

@@

%By combining the tagging, filtering and preference mechanisms, we can generate safe BGP configurations. In general, configurations are generated by combining the per-prefix configurations in the same order specified in the policy.
Figure~\ref{fig:bgp-configs} shows part of the final configuration for spine routers for the concrete and abstract policies in a vendor-neutral syntax.
%
For prefix $\True$ ($0.0.0.0/[0..32]$), the spine routers will match advertisements from peer N1 and N2. The match for N1 is preferred since it has a higher BGP local-preference attribute (110). If an advertisement from N1 is available the spine uses this and attaches the community tag $(1,0)$ before sending the route to all its peers ({\large $*$}). If an advertisement is only available from the backup N2, then it attaches the tag $(0,1)$ instead.
%
The template configuration matches any global prefix $\CD{\$GP}$ from any internal peer and re-advertise the route to all of its peers ($*$). For any local prefix it will allow an advertisement from any internal peer, and re-advertise the route to only other internal peers. The concrete configurations have a similar configuration for each local and global prefix.
